---
title: "And/Or Detection"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{And/Or Detection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(strex)
```

## How it works

`strex` offers easy and/or versions of `stringr::str_detect()` via `str_detect_all()` and `str_detect_any()`. These are vectorized over `string` but not `pattern`. `stringr::fixed()` and `stringr::coll())` are handled correctly. Otherwise, `stringr` regular expressions are used. For `str_detect_all()`, a pattern argument `c("x", "y")` is converted to `"(?=.*x)(?=.*y)"`. For `str_detect_any()`, a pattern argument `c("x", "y")` is converted to `"x|y"`. 

## Examples

```{r examples}
str_detect_all("quick brown fox", c("x", "y", "z"))
str_detect_all(c(".", "-"), ".")
str_detect_all(c(".", "-"), coll("."))
str_detect_all(c(".", "-"), coll("."), negate = TRUE)
str_detect_all(c(".", "-"), c(".", ":"))
str_detect_all(c(".", "-"), coll(c(".", ":")))
str_detect_all("xyzabc", c("a", "c", "z"))
str_detect_all(c("xyzabc", "abcxyz"), c(".b", "^x"))
str_detect_any("quick brown fox", c("x", "y", "z"))
str_detect_any(c(".", "-"), ".")
str_detect_any(c(".", "-"), coll("."))
str_detect_any(c(".", "-"), coll("."), negate = TRUE)
str_detect_any(c(".", "-"), c(".", ":"))
str_detect_any(c(".", "-"), coll(c(".", ":")))
str_detect_any(c("xyzabc", "abcxyz"), c(".b", "^x"))
```

## Performance

Unless you're doing a huge amount of computation, it won't matter, but FWIW, it's faster to convert to regex using `str_escape()` rather than using `coll()`.

```{r performance}
bench::mark(
  str_detect_all(rep("*", 1000), rep(str_escape("*"), 555)),
  str_detect_all(rep("*", 1000), coll(rep("*", 555))),
  min_iterations = 100
)
```
