---
title: "Important Miscellany"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Important Miscellany}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## The Importance of this miscellany

The features of `strex` that were deemed the _most_ interesting have been given their own vignettes. However, the package was intended as a miscellany of useful functions, so the functions demonstrated here encapsulate the spirit of this package, i.e. functions that save R string manipulators time.

```{r load}
library(strex)
```


## Could this be numeric?

Sometimes you don't want to know whether something is numeric, just whether or not it could be. Now you can find out with `str_can_be_numeric()`.

```{r can-be-numeric}
str_can_be_numeric(c("1a", "abc", "5", "2e7", "seven"))
```


## Currency

To get currencies and amounts mentioned in strings, there are `str_get_currency()` and `str_get_currencies()`. `str_get_currency()` just returns the first seen currency symbol (really just the character before the first number). `str_get_currencies()` returns all currencies and amounts mentioned in a string. `str_get_currencies()` only takes arguments of length 1, so to use it with multiple strings, you'll need to use `purrr::map()`.

```{r, error=TRUE}
string <- c("Alan paid £5", "Joe paid $7")
str_get_currency(string)
string <- c("€1 is $1.17", "£1 is $1.29")
str_get_currency(string)  # only gets the first mentioned
str_get_currencies(string[1])
purrr::map(string, str_get_currencies)
```


## Extract a single element of a string

This is a simple wrapper around `stringr::str_sub()`.

```{r str-elem}
string = "abcdefg"
str_sub(string, 3, 3)
str_elem(string, 3)  # simpler and more exressive
```


## Extract numbers and non-numeric elements

```{r extract-num-non-num}
string <- c("aa1bbb2ccc3", "xyz7ayc8jzk99elephant")
str_extract_numbers(string)
str_extract_non_numerics(string)
```


## Split a string by its numbers

```{r split-by-nums}
string <- c("aa1bbb2ccc3", "xyz7ayc8jzk99elephant")
str_split_by_nums(string)
```


## Force a file name to have an extension

We can give files a given extension, leaving them alone if they already have it.
```{r giv-ext}
string <- c("spreadsheet1.csv", "spreadsheet2")
str_give_ext(string, "csv")
```

If the file already has an extension, we can append one or replace it.

```{r give-ext-replace}
str_give_ext(string, "xls")  # append
str_give_ext(string, "csv", replace = TRUE)  # replace
```


## Strip away a file extension

```{r before-last-dot}
string <- c("spreadsheet1.csv", "spreadsheet2")
str_before_last_dot(string)
```


## Remove quoted bits from a string

```{r str-remove-quoted}
string <- "I hate having these \"quotes\" in the middle of my strings."
cat(string)
str_remove_quoted(string)
```


## Split camel case

I'm not mad on CamelCase, I often want to deconstruct it.

```{r camel}
library(magrittr)
string <- c("CamelVar1", c("CamelVar2"))
str_split_camel_case(string)
string %>% 
  str_split_camel_case() %>% 
  purrr::map_chr(str_c, collapse = "_") %>% 
  str_to_lower()
```


## Convert a string to a vector

This is something I did a lot to avoid using regular expression. Don't do it for that purpose. Learn regex. https://regexone.com/ is a very good start.

```{r to-vec}
string <- "R is good."
str_to_vec(string)
```


## Trim anything, not just whitespace

What if something is needlessly surrounded by parentheses and we want to get rid of them?

```{r trim-anything}
string <- "(((Why all the parentheses?)))"
string %>% 
  str_trim_anything("(", side = "left") %>% 
  str_trim_anything(")", side = "r")
```

Note that the `pattern` argument here isn't regular expression, just plain.


## Remove duplicated bits of strings

```{r singleize}
string <- c("I often write the word *my* twice in a row in my my sentences.")
str_singleize(string, " my")
```

